Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2021-12-13 main.tex
Added one more edit from Ramesh

Mode A is characterised by slowly evolving $P_3$ values that can range from $\sim20$ to $\sim55\,P$, and drift rates in the range $-0.3$ to $-0.7^\circ/P$.
Most commonly, $P_3$ is seen to \textit{increase} over time, as the examples in Fig. \ref{fig:pulsestacks} show.
However, there is at least one clear instance in the (MJD 59094 observation where $P_3$ decreases from approximately $35$ to $24\,P$ over the course of 170 rotations.
Mode A sequences can last anywhere from a few tens to a few hundreds of pulses, although the identification of shorter sequences as Mode A sequences relies on measuring the drift rate, since in such cases the sequence is not long enough to measure $P_3$ directly.

>>>>

Mode A is characterised by slowly evolving $P_3$ values that can range from $\sim20$ to $\sim55\,P$, and drift rates in the range $-0.3$ to $-0.7^\circ/P$.
Most commonly, $P_3$ is seen to \textit{increase} over time, as the examples in Fig. \ref{fig:pulsestacks} show.
However, there is at least one clear instance in the (MJD 59094 observation where $P_3$ decreases from approximately $35$ to $24\,P$ over the course of 170 rotations.

Mode A sequences can last anywhere from a few tens to a few hundreds of pulses.
For longer sequences, Mode A is easily identifiable from the relatively large $P_3$, but for shorter sequences, only one or two drift bands are visible, and therefore $P_3$ cannot be measured directly.
In these cases, a positive identification of Mode A is based on the drift rate, which can be measured even for single drift bands.
